Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1 and ERC project 280053 (CPROVER).}

### 2017-02-02 hscc2017/paper.tex
line breaks
reviewed 3.5 Soundness

\subsection{Soundness}
The soundness of the model is ensured by the {\sc verify} phase. The {\sc synthesise} phase is only concerned with providing a candidate solution that is not ensured to work for any of the plant models. However, it is increasingly likely to be correct as the system loops through counterexamples. The overall result is that if a candidate solution is validated by the verifier, it is necessarily sound, otherwise we may simply not find a valid solution in the given time.
The {\sc verify} phase looks at two separate elements for soundness. The first corresponds to the fitness of the controller for all plant models. This phase ensures that there exists no counterexample plant that would create a closed loop with unstable poles. The fixed word length of the controller is not relevant at this point since the parameters have already been chosen to fit this criteria (\emph{ie} the candidate solution is FWL). The model is verified using the SAT solver backend in cbmc, which looks for the satisfiability of a plant with an unstable closed loop. If no counterexample is found, then the controller is necessarily stable for all plants in the collection. The limitation of this approach is the data type used by the verifier to perform the evaluation. Since the actual plant works in the reals, whereas we use fixed/floating point arithmetic to evaluate it, we need to ensure that the rounding errors in the caculations do not cause the solution to be unsound. For this reason the second verification phase uses interval arithmetic with outward rounding to ensure that these errors do not exceed critical bounds that could make some (or all) plant(s) unstable. This means that whilst the solution may not be complete, it is sound for evaluating any collection of real plants with a defined FWL controller for all of them. The need for two verification phases is because whereas this second phase can ensure the stability of all plants in the collection, it is unable to provide a counterexample.

>>>>

%-----------------------------
\subsection{Soundness}
%-----------------------------

The soundness of the model is ensured by the {\sc verify} phase. The {\sc synthesise} phase is only concerned with providing a candidate solution that is not ensured to work for any of the plant models. However, it is increasingly likely to be correct as the system loops through counterexamples. The overall result is that if a candidate solution is validated by the verifier, it is necessarily sound; otherwise, we may simply not find a valid solution in the given time.
The {\sc verify} phase looks at two separate elements for soundness. The first corresponds to the fitness of the controller for all plant models. This phase ensures that there exists no counterexample plant that would create a closed-loop with unstable poles. The fixed word length of the controller is not relevant at this point since the parameters have already been chosen to fit this criteria (i.e., the candidate solution is FWL). The model is verified using the SAT solver backend in CBMC, which looks for the satisfiability of a plant with an unstable closed loop. If no counterexample is found, then the controller is necessarily stable for all plants in the collection. The limitation of this approach is the data type used by the verifier to perform the evaluation. Since the actual plant works in the reals, whereas we use fixed/floating point arithmetic to evaluate it, we need to ensure that the rounding errors in the caculations do not cause the solution to be unsound. For this reason the second verification phase uses interval arithmetic with outward rounding to ensure that these errors do not exceed critical bounds that could make some (or all) plant(s) unstable. This means that whilst the solution may not be complete, it is sound for evaluating any collection of real plants with a defined FWL controller for all of them. The need for two verification phases is because whereas this second phase can ensure the stability of all plants in the collection, it is unable to provide a counterexample.
